Analyzing DECREASE trials for extent of data fabrication

### 2016-04-29 submission/manuscript.Rmd
Minor manuscript adjustment
Rerun with Likelihood as endpoint for step 3

bouri_data <- read.csv('../data/bouri_data.csv')
bouri_data <- read.csv('data/bouri_data.csv')

@@

iterations <- 1000

# Uncomment if you want to rerun the inversion method
# > t1
# [1] "2016-03-29 13:34:31 CEST"
# > t2
# [1] "2016-03-29 15:55:27 CEST"
# t1 <- Sys.time()
# source('../functions/inversion_method_uncertain.R')
# source('../functions/inversion_method_certain.R')
# t2 <- Sys.time()

@@

load('../data/result_almost_iv_uncertain')
load('../data/result_almost_iv_certain')

# load('data/result_almost_i_uncertain')
# load('data/result_almost_i_certain')
# 
# load('data/result_almost_iv_uncertain')
# load('data/result_almost_iv_certain')

>>>>

bouri_data <- read.csv('../data/bouri_data.csv')
# bouri_data <- read.csv('data/bouri_data.csv')

@@

iterations <- 10000

# Uncomment if you want to rerun the inversion method
# > t1
# [1] "2016-03-29 13:34:31 CEST"
# > t2
# [1] "2016-03-29 15:55:27 CEST"
# t1 <- Sys.time()
# source('../functions/inversion_method_uncertain.R')
# # source('functions/inversion_method_uncertain.R')
# t2 <- Sys.time()
# source('../functions/inversion_method_certain.R')
# # source('functions/inversion_method_certain.R')
# t3 <- Sys.time()

@@

load('../data/result_almost_iv_uncertain')
load('../data/result_almost_iv_certain')
# 
# load('data/result_almost_i_uncertain')
# load('data/result_almost_i_certain')
# 
# load('data/result_almost_iv_uncertain')
# load('data/result_almost_iv_certain')
